A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)

### 2018-04-10 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

\title{A Reduced Order Model for Permeability Fields Using Singular Value Decomposition, SVD}
\author[UoA]{B. Lashore\corref{cor1}}\ead{lashorebabatunde@yahoo.com} \author[UoA]{K. Christou} \author[UoA]{J.L.M.A. Gomes} 
\cortext[cor1]{Corresponding author.}
\address[UoA]{Mechanics of Fluids, Soils \& Structures Research Group \\ School of Engineering University of Aberdeen, UK}

@@

In this paper, a method for applying SVD to reduced the order of (\ie upscale) the permeability field (of a BaseCase) was introduced. This method was compared to arithmetic and harmonic averaging (\ie upscaling) technique as well as a stochastic probability density function (PDF) method of upscaling, to highlight its benefits. It was shown that the SVD upscaling technique retained the heterogenous nature of the BaseCase. Additionally, the SVD upscaling technique did not require a priori understanding of similar permeability blocks within the existing domain (\ie the BaseCase).

>>>>

\title{A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)}
\author[UoA]{B. Lashore\corref{cor1}}\ead{lashorebabatunde@yahoo.com} \author[UoA]{K. Christou} \author[UoA]{J.L.M.A. Gomes} 
\cortext[cor1]{Corresponding author.}
\address[UoA]{Mechanics of Fluids, Soils \& Structures Research Group \\ School of Engineering, University of Aberdeen, UK}

@@

\red{Motivation for the work? What is the main aim of the work?} In this paper, a method for applying SVD to reduced the order of (\ie upscale) the permeability field (of a BaseCase) was introduced. This method was compared to arithmetic and harmonic averaging (\ie upscaling) technique as well as a stochastic probability density function (PDF) method of upscaling, to highlight its benefits. It was shown that the SVD upscaling technique retained the heterogenous nature of the BaseCase. Additionally, the SVD upscaling technique did not require a priori understanding of similar permeability blocks within the existing domain (\ie the BaseCase).
